ICM testing

### 2023-10-24 Scripts/ASR_stocks.Rmd
Tuning fixes completed
Everything appears to be working A-OK now, last big fix was fixing the r value coming from the Euler-Lotka model, it needs to be exp(r) to make it = lambda, then simply used lambda in the models

```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)
library(cowplot)
loc <- 'C:/Users/Owner/Documents/GitHub/ICM'

source(paste0(loc,"/Scripts/functions/backwards_sim.R"))
source(paste0(loc,"/Scripts/functions/tuning_sim.R"))

@@

  #r.p.ssb This needs to be offset by the age of recruits
  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+1):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage)])
  # recs.per.age
  data <- left_join(data, annual)
  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
  tmp <- NULL
  for(j in 1:length(years))
  {
    tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
    tst$Year <- tst$Year + minage
    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
    tmp[[j]] <- tst
  }
  # Unpack the list
  ssb.off <- do.call('rbind',tmp)
  # And merge it with the data object
  data <- left_join(data,ssb.off,by=c("Year","age"))
  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
  # mx
  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
  # This works because 'males' is also in 'females'
  if(grepl("males",i)) data$mx <- data$recs.per.age/data$ssn.offset 
  if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
  # Easier to remove the years where we don't have recs.per.age...
  #data <- data %>% dplyr::filter(Year %in% years[(minage+1):length(years)])
  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...

@@

  tst <- back.sim(years,
                 mat.age = age.mat,
                 nm = -(log(1-prop.nat.mort)),
                 w.age = weight.age,
                 ages = ages,
                 rems = rem$rem,
                 fecund = mx,
                 N.end = N.end,
                 pop.model = 'exponential',
                 n.sims = 50,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)

@@

# ################# Now run as a forward simulation
#   N.start <- vpa.abund[1] 
# 
#   tst <- for.sim(years,
#                  mat.age = age.mat,
#                  nm = -(log(1-prop.nat.mort)),
#                  w.age = weight.age,
#                  ages = ages,
#                  rems = rem$rem, # rep(0,nrow(rem)),
#                  fecund = mx,
#                  N.start = N.start,
#                  pop.model = 'exponential', K = 2e6,
#                  n.sims = 2,
#                  sd.mat = 0.5,
#                  sd.nm = 0.5,
#                  sd.wt = 0.5,
#                  sd.fecund = 0.5)
# 
#   #Combine the data
#   did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
#   # Here get the Upper and lower 50% quantiles to make a functional boxplot
#   quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
#                                                                         med = median(abund),
#                                                                         U.50 = quantile(abund,probs=c(0.75)))
# 
#   for.res[[i]] <- tst
#   for.ts[[i]] <- did.it.work
#   for.ts.quants[[i]] <- quants

# ########################## Now run the tuning sims
# #
#    N.end <- vpa.abund[length(vpa.abund)]
#    tunes <- tune.sim(years,
#                      n.steps = 100,
#                      abund.ts = vpa.abund,
#                      mat.age = age.mat,
#                      nm = -(log(1-prop.nat.mort)),
#                      w.age = weight.age,
#                      ages = ages,
#                      rems = rem$rem,
#                      fecund = mx,
#                      N.end = N.end,
#                      pop.model = 'exponential')
# 
#    tuned.res[[i]] <- tunes
} # end i in Stocks look

# Save all these
# saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
 saveRDS(object = back.res,file = paste0(loc,"/Results/backwards_sim_results.Rds"))
 saveRDS(object = back.ts,file = paste0(loc,"/Results/backwards_sim_ts_summaries.Rds"))
 saveRDS(object = back.ts.quants,file = paste0(loc,"/Results/backwards_sim_ts_quantiles_summaries.Rds"))
```

@@

# Now we can run the figures separately.
tuned.res <- readRDS(file = "D:/Github/ICM/Results/tuned_fits.Rds")
back.ts <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
back.ts.quants <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
back.res <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
load(file = "D:/Github/ICM/Results/model_inputs.Rdata")

>>>>

```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)
library(cowplot)
loc <- 'D:/GitHub/ICM'

source(paste0(loc,"/Scripts/functions/backwards_sim.R"))
source(paste0(loc,"/Scripts/functions/forward_sim.R"))
source(paste0(loc,"/Scripts/functions/tuning_sim.R"))

@@

  #r.p.ssb This needs to be offset by the age of recruits
  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+1):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage)])
  # recs.per.age
  data <- left_join(data, annual)
  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
  tmp <- NULL
  for(j in 1:length(years))
  {
    tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
    tst$Year <- tst$Year + minage
    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
    tmp[[j]] <- tst
  }
  # Unpack the list
  ssb.off <- do.call('rbind',tmp)
  # And merge it with the data object
  data <- left_join(data,ssb.off,by=c("Year","age"))
  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
  # mx
  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
  # Easier to remove the years where we don't have recs.per.age...
  #data <- data %>% dplyr::filter(Year %in% years[(minage+1):length(years)])
  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...

@@

  # The first run gives us the mean estimate, I think that's all we need for our first paper
  tst <- back.sim(years,
                 mat.age = age.mat,
                 nm = -(log(1-prop.nat.mort)),
                 w.age = weight.age,
                 ages = ages,
                 rems = rem$rem,
                 fecund = mx,
                 N.end = N.end,
                 pop.model = 'exponential',
                 n.sims = 100,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)

@@

# ################# Now run as a forward simulation
N.start <- vpa.abund[1]

tst <- for.sim(years,
               mat.age = age.mat,
               nm = -(log(1-prop.nat.mort)),
               w.age = weight.age,
               ages = ages,
               rems = rem$rem, # rep(0,nrow(rem)),
               fecund = mx,
               N.start = N.start,
               pop.model = 'exponential',
               n.sims = 100,
               sd.mat = 0.5,
               sd.nm = 0.5,
               sd.wt = 0.5,
               sd.fecund = 0.5)

  for.res[[i]] <- tst
  for.ts[[i]] <- did.it.work
  for.ts.quants[[i]] <- quants

# Save all these
# saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
saveRDS(object = back.res,file = paste0(loc,"/Results/backwards_sim_results.Rds"))
saveRDS(object = back.ts,file = paste0(loc,"/Results/backwards_sim_ts_summaries.Rds"))
saveRDS(object = back.ts.quants,file = paste0(loc,"/Results/backwards_sim_ts_quantiles_summaries.Rds"))
saveRDS(object = for.res,file = paste0(loc,"/Results/forwards_sim_results.Rds"))
saveRDS(object = for.ts,file = paste0(loc,"/Results/forwards_sim_ts_summaries.Rds"))
saveRDS(object = for.ts.quants,file = paste0(loc,"/Results/forwards_sim_ts_quantiles_summaries.Rds"))

@@

# Now we can run the figures separately.
# tuned.res <- readRDS(file = "D:/Github/ICM/Results/tuned_fits.Rds")
back.ts <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
back.ts.quants <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
back.res <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
load(file = "D:/Github/ICM/Results/model_inputs.Rdata")
